---
title: "De-identifying data from the SLPA survey"
author: "Sur Herrera Paredes"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
params:
  full_survey: "data/2022-09-22.full_survey.csv"
  min_n: 5
  outdir: "public_data"
---

This document contains the code to process the raw answerts to the
the SLPA Moving & Living Expenses Survey 2022, and produce a set of 
files that can be used for further analysis while trying to prevent
de-identification of the respondents. To be clear, the steps taken here
do no guarantee that de-identification is impossible, but should make it
significantly harder. The input to this R Markdown script should not
be shared with anyone outside the SLPA team working directly on the results.

The next steps are taken to try to make de-identification harder:

1. Timestamps are removed if they are still in the input.
2. For each question, all responses are saved in a separate file, and the
order of the responses is scrambled independently to avoid matching. Scrambling
is done with seeds from random.org.
3. For every question, when some group of responses is of a size less than 
`r params$min_n`, those responses are re-coded re-coded so we can report them
with groups above this threshold.
4. For cross-tabulations of interest. A file matching responses for multiple
questions is only created if answers can be re-coded logically and maintaining
the minimum group size of `r params$min_n`.

# Setup

Load required libraries

```{r libraries}
library(tidyverse)
library(random)
```

```{r functions}
write_question_answers <- function(Dat, col, outdir){
  seed <- randomNumbers(n = 1, min = 1, max = 1000, col = 1)[1,1]
  dat <- drop_na(Dat[ , col])
  set.seed(seed)
  ii <- sample(1:nrow(dat), replace = FALSE)
  dat <- dat[ii,]
  
  filename <- file.path(outdir, paste0("Q", col, ".tsv"))
  write_tsv(dat, filename, quote = 'all')
  cat(paste0("Wrote Q", col, " into ", filename, "\n"))
}

write_crosstab <- function(Dat, outdir){
  seed <- randomNumbers(n = 1, min = 1, max = 1000, col = 1)[1,1]
  dat <- drop_na(Dat)
  set.seed(seed)
  ii <- sample(1:nrow(dat), replace = FALSE)
  dat <- dat[ii,]
  
  filename <- file.path(outdir,
                        paste0(paste0(colnames(dat),collapse = "_"), ".tsv"))
  write_tsv(dat, filename, quote = 'all')
  cat(paste0("Wrote ", paste(colnames(dat), collapse = " "), " into ", filename, "\n"))
}

```


Prepare output directory. The output of that directory can be shared
with other people interested in analysis. The SLPA leadership must give 
approval though. Special care should be given to open ended questions
since some answers might de-identify respondents.

```{r create outdir}
dir.create(params$outdir)
dir.create(file.path(params$outdir, "closed_questions"))
dir.create(file.path(params$outdir, "open_questions"))
```

# Read data

We read the data and print the questions (headers of the csv)
```{r read data}
Dat <- read_csv(params$full_survey,
                col_types = 'c')
```

If timestamp exists we remove it

```{r remove timestamps}
ii <- colnames(Dat) %>% str_detect(regex("Timestamp", ignore_case = TRUE), negate = TRUE)
Dat <- Dat[,ii]
```
Now we list the questions
```{r qeustions}
filename <- file.path(params$outdir, "questions.tsv")
tibble(id = paste0("Q", 1:ncol(Dat)),
       question = colnames(Dat)) %>%
  write_tsv(filename)
colnames(Dat)
```

# Questions

## `r colnames(Dat)[1]`

```{r "Q `r colnames(Dat)[1]`"}
col <- 1
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  stop("ERROR: No recode rules")
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[2]`

```{r "Q `r colnames(Dat)[2]`"}
col <- 2
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  vals <- table(Dat[, col])
  to_replace <- names(vals)[ vals < params$min_n ]
  
  if( sum(vals[ to_replace ]) >= params$min_n ){
    Dat[ ,col ] <- replace(Dat[, col, drop = TRUE], Dat[, col, drop = TRUE] %in% to_replace, "Other")
    write_question_answers(Dat = Dat, col = col, outdir = outdir)
  }else{
    stop("Recode rule not working")
  }
  
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[3]`

```{r "Q `r colnames(Dat)[3]`"}
col <- 3
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  # First order responses
  Dat[,col] <- factor(Dat[,col, drop = TRUE],
                      levels = c("$300-$600",
                                 "$601-$1000",
                                 "$1001-$1700",
                                 "$1701-$2500",
                                 "$2500-$3000",
                                 "more than $3000"))


  vals <- table(Dat[, col])
  i <- 1
  while(any(vals < params$min_n)){
    if(vals[i] < params$min_n){
      if(i == length(vals)){
        stop("MERGE RULE MISSING")
      }else{
        # Get new range
        start <- str_split(names(vals)[i], "[- ]")[[1]][1]
        end <- str_split(names(vals)[i + 1], "[- ]")[[1]]
        
        if(end[1] == "more"){
          new_val <- paste0("more than", start)
        }else{
          end <- end[length(end)]
          new_val <- paste0(start, "-", end)
        }
        
        # Substitute new range
        dat <- Dat[,col,drop=TRUE]
        levels(dat)[i] <- levels(dat)[i + 1]
        levels(dat)[i] <- new_val
        Dat[,col] <- dat
        
        i <- i - 1
      }
    }
    
    vals <- table(Dat[, col])
    i <- i + 1
    i <- i %% length(vals)
    
  }
 
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[4]`

```{r "Q `r colnames(Dat)[4]`"}
col <- 4
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  stop("ERROR: No recode rules")
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[5]`

```{r "Q `r colnames(Dat)[5]`"}
col <- 5
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  # First order responses
  # vals <- table(Dat[, col])
  # vals
  Dat[,col] <- factor(Dat[,col, drop = TRUE],
                      levels = c("Did not pay rent",
                                 "less than $100",
                                 "$101-$500",
                                 "$501-$1000",
                                 "$1001-$2000",
                                 "more than $2000"))


  vals <- table(Dat[, col])
  vals
  i <- 1
  while(any(vals < params$min_n)){
    if(vals[i] < params$min_n){
      if(i == length(vals)){
        stop("MERGE RULE MISSING")
      }else{
        # Get new range
        start <- str_split(names(vals)[i], "[- ]")[[1]]
        if(start[1] == "less"){
          start <- "less than"
          sepchar <- " "
        }else if(start[1] == "Did"){
          start <- "$0"
          sepchar <- "-"
        }else{
          start <- start[1]
          sepchar <- "-"
        }
        
        end <- str_split(names(vals)[i + 1], "[- ]")[[1]]
        
        if(end[1] == "more"){
          new_val <- paste0("more than ", start)
        }else{
          end <- end[length(end)]
          new_val <- paste0(start, sepchar , end)
        }
        
        # Substitute new range
        dat <- Dat[,col,drop=TRUE]
        levels(dat)[i] <- levels(dat)[i + 1]
        levels(dat)[i] <- new_val
        Dat[,col] <- dat
        
        i <- i - 1
      }
    }
    
    vals <- table(Dat[, col])
    i <- i + 1
    i <- i %% length(vals)
    
  }
  table(Dat[,col])
 
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[6]`

```{r "Q `r colnames(Dat)[6]`"}
col <- 6
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  # First order responses
  # vals <- table(Dat[, col])
  # vals
  Dat[,col] <- factor(Dat[,col, drop = TRUE],
                      levels = c("$1000-$2000",
                                 "$2001-$3000",
                                 "$3001-$4000",
                                 "$4001-$5000",
                                 "$5000-$6000",
                                 "more than $6000"))


  vals <- table(Dat[, col])
  # vals
  i <- 1
  while(any(vals < params$min_n)){
    if(vals[i] < params$min_n){
      if(i == length(vals)){
        stop("MERGE RULE MISSING")
      }else{
        # Get new range
        start <- str_split(names(vals)[i], "[- ]")[[1]]
        if(start[1] == "less"){
          start <- "less than"
          sepchar <- " "
        }else if(start[1] == "Did"){
          start <- "$0"
          sepchar <- "-"
        }else{
          start <- start[1]
          sepchar <- "-"
        }
        
        end <- str_split(names(vals)[i + 1], "[- ]")[[1]]
        
        if(end[1] == "more"){
          new_val <- paste0("more than ", start)
        }else{
          end <- end[length(end)]
          new_val <- paste0(start, sepchar , end)
        }
        
        # Substitute new range
        dat <- Dat[,col,drop=TRUE]
        levels(dat)[i] <- levels(dat)[i + 1]
        levels(dat)[i] <- new_val
        Dat[,col] <- dat
        
        i <- i - 1
      }
    }
    
    vals <- table(Dat[, col])
    i <- i + 1
    i <- i %% length(vals)
    
  }
  table(Dat[,col])
 
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}

```

## `r colnames(Dat)[7]`

```{r "Q `r colnames(Dat)[7]`"}
col <- 7
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  # First order responses
  # vals <- table(Dat[, col])
  # vals
  Dat[,col] <- factor(Dat[,col, drop = TRUE],
                      levels = c("less than $500",
                                 "$500-$1000",
                                 "$1001-$1500",
                                 "$1501-$2000",
                                 "$2001-$2500",
                                 "$2501-$3000",
                                 "more than $3000"))


  vals <- table(Dat[, col])
  vals
  i <- 1
  while(any(vals < params$min_n)){
    if(vals[i] < params$min_n){
      if(i == length(vals)){
        stop("MERGE RULE MISSING")
      }else{
        # Get new range
        start <- str_split(names(vals)[i], "[- ]")[[1]]
        if(start[1] == "less"){
          start <- "less than"
          sepchar <- " "
        }else if(start[1] == "Did"){
          start <- "$0"
          sepchar <- "-"
        }else{
          start <- start[1]
          sepchar <- "-"
        }
        
        end <- str_split(names(vals)[i + 1], "[- ]")[[1]]
        
        if(end[1] == "more"){
          new_val <- paste0("more than ", start)
        }else{
          end <- end[length(end)]
          new_val <- paste0(start, sepchar , end)
        }
        
        # Substitute new range
        dat <- Dat[,col,drop=TRUE]
        levels(dat)[i] <- levels(dat)[i + 1]
        levels(dat)[i] <- new_val
        Dat[,col] <- dat
        
        i <- i - 1
      }
    }
    
    vals <- table(Dat[, col])
    i <- i + 1
    i <- i %% length(vals)
    
  }
  table(Dat[,col])
 
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}

```

## `r colnames(Dat)[8]`

```{r "Q `r colnames(Dat)[8]`"}
col <- 8
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  stop("ERROR: No recode rules")
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[9]`

```{r "Q `r colnames(Dat)[9]`"}
col <- 9
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  vals <- table(Dat[, col])
  to_replace <- names(vals)[ vals < params$min_n ]
  
  if( sum(vals[ to_replace ]) >= params$min_n ){
    Dat[ ,col ] <- replace(Dat[, col, drop = TRUE], Dat[, col, drop = TRUE] %in% to_replace, "Other")
    write_question_answers(Dat = Dat, col = col, outdir = outdir)
  }else{
    stop("Recode rule not working")
  }
  
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[10]`

```{r "Q `r colnames(Dat)[10]`"}
col <- 10
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  vals <- table(Dat[, col])
  vals
  to_replace <- names(vals)[ vals < params$min_n ]
  
  stop("NO RECODE RULE")
  
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[11]`
The way this is encoded in the google form this is an open question, though 
it should be recoded as a year set of answers

```{r "Q `r colnames(Dat)[11]`"}
col <- 11
outdir <- file.path(params$outdir, "closed_questions")

# Re code into years
dat <- Dat[,col, drop = TRUE]
dat <- replace(dat, dat == "2022 01", "2022")
dat <- replace(dat, dat == "summer 2021", "2022")
dat <- replace(dat, dat == "October 2021", "2022")
dat <- replace(dat, dat == "February 2022", "2022")
dat <- replace(dat, dat == "November 2020", "2020")
dat <- replace(dat, dat == "August 2022", "2022")
dat <- replace(dat, dat == "Nov 2020", "2020")
dat <- replace(dat, dat == "2021 (July)", "2021")
dat <- replace(dat, dat == "07/2017", "2017")
dat[ which(str_detect(dat, "; started postdoc in")) ] <- 2020
dat <- replace(dat, dat == "07/2017", "2017")
unique(dat)
if( any(!(dat %in% c("2012", "2013", "2014", "2015", 
           "2016", "2017", "2018","2019", 
           "2020", "2021", "2022", NA))) ){
  stop("ERROR: UNEXPECTED YEAR VALUE")
}
Dat[,col] <- dat
if(any(table(Dat[, col]) < params$min_n)){
  # First order responses
  # vals <- table(Dat[, col])
  # vals
  cat("Grouping\n")
  Dat[,col] <- factor(Dat[,col, drop = TRUE],
                      levels = c("2012",
                                 "2013", 
                                 "2014", "2015", 
           "2016", "2017", "2018","2019", 
           "2020", "2021", "2022")) %>% droplevels()


  vals <- table(Dat[, col])
  vals
  i <- 1
  while(any(vals < params$min_n)){
    if(vals[i] < params$min_n){
      if(i == length(vals)){
        stop("MERGE RULE MISSING")
      }else{
        # Get new range
        start <- str_split(names(vals)[i], "[- ]")[[1]]
        if(start[1] == "less"){
          start <- "less than"
          sepchar <- " "
        }else if(start[1] == "Did"){
          start <- "$0"
          sepchar <- "-"
        }else{
          start <- start[1]
          sepchar <- "-"
        }
        
        end <- str_split(names(vals)[i + 1], "[- ]")[[1]]
        
        if(end[1] == "more"){
          new_val <- paste0("more than ", start)
        }else{
          end <- end[length(end)]
          new_val <- paste0(start, sepchar , end)
        }
        
        # Substitute new range
        dat <- Dat[,col,drop=TRUE]
        levels(dat)[i] <- levels(dat)[i + 1]
        levels(dat)[i] <- new_val
        Dat[,col] <- dat
        
        i <- i - 1
      }
    }
    
    vals <- table(Dat[, col])
    i <- i + 1
    i <- i %% length(vals)
    
  }
  table(Dat[,col])
 
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
  
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[12]`

```{r Q12}
col <- 12
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  vals <- table(Dat[, col])
  vals
  to_replace <- names(vals)[ vals < params$min_n ]
  
  stop("NO RECODE RULE")
  
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[13]`
This question is mostly numeric in answers, though some
people provided additional details. Those details need to be saved as open
answers. And the numeric values need to be re-coded.

```{r Q13 open}
col <- 13

# First save all responses with text
outdir <- file.path(params$outdir, "open_questions")
dat <- Dat[ , col, drop = FALSE ]
dat <- dat %>%
  mutate(across(.cols = 1, 
                .fns = function(x) {
                  print(class(x))
                  x %>% str_detect("[a-zA-z]")},
                .names = "ii")) %>%
  filter(ii) %>% select(-ii)

# Add dummy vars
for(i in 1:(col - 1)){
  dat <- bind_cols("a",
            dat)
}
write_question_answers(Dat = dat, col = col, outdir = outdir)
```

Now the numeric part of this question

```{r "Q `r colnames(Dat)[13]`"}
col <- 13
outdir <- file.path(params$outdir, "closed_questions")
dat <- Dat[ , col, drop = TRUE ]

# First re-code numeric inputs
dat <- dat %>%
  str_replace(pattern = "^\\$([0-9]+)$", replacement = "\\1") %>%
  str_replace(pattern = "^~([0-9]+)$", replacement = "\\1") %>%
  str_replace(pattern = "^~\\$([0-9]+)$", replacement = "\\1") %>%
  str_replace(pattern = "^~([0-9]+)[.]00$", replacement = "\\1") %>%
  str_replace(pattern = "^([0-9]+) dollars$", replacement = "\\1")  %>%
  str_replace(pattern = "^\\$([0-9]+) for both cars$", replacement = "\\1") %>%
  str_replace(pattern = "^([0-9]+) \\(I mostly bike\\)$", replacement = "\\1") %>%
  str_replace(pattern = "^([0-9]+) USD$", replacement = "\\1") %>%
  str_replace(pattern = "^I bike. So zero$", replacement = "0") %>%
  str_replace(pattern = "^\\$([0-9]+) \\(bicycle maintenance\\)$", replacement = "\\1") 
dat

# Manually modify NA cases (saved as text)
ii <- which(str_detect(dat, fixed("negligible / changes (I bike & caltrain to work w/ Go Pass)")))
dat[ii] <- NA
ii <- which(str_detect(dat, fixed("+500")))
dat[ii] <- "500"
ii <- which(str_detect(dat, fixed("Car not affordable")))
dat[ii] <- NA
ii <- which(str_detect(dat, fixed("I bike to campus, use the car rarely")))
dat[ii] <- NA
ii <- which(str_detect(dat, fixed("~$250-300")))
dat[ii] <- "250-300"
ii <- which(str_detect(dat, fixed("Less than $10")))
dat[ii] <- "5"
ii <- which(str_detect(dat, fixed("not sure (have been here less than a month)")))
dat[ii] <- NA

ii <- which(str_detect(dat, fixed("UBER")))
dat[ii] <- NA
dat

# Get mean of ranges
ii <- which(dat %>% str_detect("^[0-9]+-[0-9]+$"))
ranges <- dat[ii]
ranges <- ranges %>% 
  str_split("-") %>%
  map_dbl(function(x){
    x <- as.numeric(x)
    sum(x) / length(x)})
dat[ii] <- ranges  
# Remove anything left with text
ii <- which(dat %>% str_detect("[a-zA-z]"))
dat[ii] <- NA
dat <- as.numeric(dat)

dat <- cut(c(dat), breaks = c(0, 100, 200, 300,500, max(dat, na.rm = TRUE)))
levels(dat) <- c("less than $100",
                 "$101-$200",
                 "$201-$300",
                 "$301-$500",
                 "more than $500")
Dat[ ,col ] <- dat
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  vals <- table(Dat[, col])
  vals
  to_replace <- names(vals)[ vals < params$min_n ]
  
  stop("NO RECODE RULE")
  
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[14]`

```{r Q14"}
col <- 14
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  
  dat <- Dat[,col, drop = TRUE]
  ii <- which(dat >= 3)
  dat <- as.character(dat)
  dat[ii] <- "3 or more"
  Dat[,col] <- dat
  
  if(any(table(Dat[, col]) < params$min_n)){
    stop("Grouping insufficient", call. = TRUE)
  }
  
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[15]`

```{r Q15"}
col <- 15
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  vals <- table(Dat[, col])
  vals
  to_replace <- names(vals)[ vals < params$min_n ]
  
  stop("ERROR: No recode rules")
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[16]`

```{r Q16}
col <- 16
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  # First order responses
  # vals <- table(Dat[, col])
  # vals
  cat("Grouping\n")
  Dat[,col] <- factor(Dat[,col, drop = TRUE],
                      levels = c("$500-$1000",
                                 "$1001-$1500",
                                 "$1501-$2000",
                                 "$2001-$2500",
                                 "$2500-$3000",
                                 "more than $3000"))


  vals <- table(Dat[, col])
  vals
  i <- 1
  while(any(vals < params$min_n)){
    if(vals[i] < params$min_n){
      if(i == length(vals)){
        stop("MERGE RULE MISSING")
      }else{
        # Get new range
        start <- str_split(names(vals)[i], "[- ]")[[1]]
        if(start[1] == "less"){
          start <- "less than"
          sepchar <- " "
        }else if(start[1] == "Did"){
          start <- "$0"
          sepchar <- "-"
        }else{
          start <- start[1]
          sepchar <- "-"
        }
        
        end <- str_split(names(vals)[i + 1], "[- ]")[[1]]
        
        if(end[1] == "more"){
          new_val <- paste0("more than ", start)
        }else{
          end <- end[length(end)]
          new_val <- paste0(start, sepchar , end)
        }
        
        # Substitute new range
        dat <- Dat[,col,drop=TRUE]
        levels(dat)[i] <- levels(dat)[i + 1]
        levels(dat)[i] <- new_val
        Dat[,col] <- dat
        
        i <- i - 1
      }
    }
    
    vals <- table(Dat[, col])
    i <- i + 1
    i <- i %% length(vals)
    
  }
  table(Dat[,col])
 
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}

```

## `r colnames(Dat)[17]`

```{r Q17}
col <- 17
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  # First order responses
  # vals <- table(Dat[, col])
  # vals
  cat("Grouping\n")
  Dat[,col] <- factor(Dat[,col, drop = TRUE],
                      levels = c("less then $100",
                                 "$101-$300",
                                 "$301-$500",
                                 "$501-$700",
                                 "more than $700"))
  #!!!!
  dat <- Dat[,col,drop = TRUE]
  levels(dat)[1] <- "less than $100"
  Dat[,col] <- dat

  vals <- table(Dat[, col])
  # vals
  i <- 1
  while(any(vals < params$min_n)){
    if(vals[i] < params$min_n){
      if(i == length(vals)){
        stop("MERGE RULE MISSING")
      }else{
        # Get new range
        start <- str_split(names(vals)[i], "[- ]")[[1]]
        if(start[1] == "less"){
          start <- "less than"
          sepchar <- " "
        }else if(start[1] == "Did"){
          start <- "$0"
          sepchar <- "-"
        }else{
          start <- start[1]
          sepchar <- "-"
        }
        
        end <- str_split(names(vals)[i + 1], "[- ]")[[1]]
        
        if(end[1] == "more"){
          new_val <- paste0("more than ", start)
        }else{
          end <- end[length(end)]
          new_val <- paste0(start, sepchar , end)
        }
        
        # Substitute new range
        dat <- Dat[,col,drop=TRUE]
        levels(dat)[i] <- levels(dat)[i + 1]
        levels(dat)[i] <- new_val
        Dat[,col] <- dat
        
        i <- i - 1
      }
    }
    
    vals <- table(Dat[, col])
    i <- i + 1
    i <- i %% length(vals)
    
  }
  table(Dat[,col])
  
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}

```
## `r colnames(Dat)[18]`

```{r Q18 open}
col <- 18
outdir <- file.path(params$outdir, "open_questions")
write_question_answers(Dat = Dat, col = col, outdir = outdir)
```


## `r colnames(Dat)[19]`

```{r Q19}
col <- 19
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  vals <- table(Dat[, col])
  vals
  to_replace <- names(vals)[ vals < params$min_n ]
  to_replace <- c(to_replace, "Other")

  
  if( sum(vals[ to_replace ]) >= params$min_n ){
    Dat[ ,col ] <- replace(Dat[, col, drop = TRUE], Dat[, col, drop = TRUE] %in% to_replace, "Other")
    write_question_answers(Dat = Dat, col = col, outdir = outdir)
  }else{
    stop("Recode rule not working")
  }
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[20]`

```{r Q20}
col <- 20
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  cat("Grouping\n")
  vals <- table(Dat[, col])
  vals
  # to_replace <- names(vals)[ vals < params$min_n ]
  to_replace <- c("4", "5")
  if(all(vals[to_replace] > params$min_n)){
    stop("NO NEED TO AGGREGATE")
  }
  
  if( sum(vals[ to_replace ]) >= params$min_n ){
    Dat[ ,col ] <- replace(Dat[, col, drop = TRUE], Dat[, col, drop = TRUE] %in% to_replace, "4-5")
    write_question_answers(Dat = Dat, col = col, outdir = outdir)
  }else{
    stop("Recode rule not working")
  }
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[21]`

```{r Q21"}
col <- 21
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  vals <- table(Dat[, col])
  vals
  to_replace <- names(vals)[ vals < params$min_n ]
  
  stop("ERROR: No recode rules")
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```

## `r colnames(Dat)[22]`

```{r Q22"}
col <- 22
outdir <- file.path(params$outdir, "closed_questions")
if(any(table(Dat[, col]) < params$min_n)){
  vals <- table(Dat[, col])
  vals
  to_replace <- names(vals)[ vals < params$min_n ]
  
  stop("ERROR: No recode rules")
}else{
  write_question_answers(Dat = Dat, col = col, outdir = outdir)
}
```
## `r colnames(Dat)[23]`

```{r Q23 open}
col <- 23
outdir <- file.path(params$outdir, "open_questions")
write_question_answers(Dat = Dat, col = col, outdir = outdir)
```

# Cross tabulations

First create directory for cross tabs

```{r}
dir.create(file.path(params$outdir, "crosstabs"))
```


# Q1 & Q2
```{r}
cols <- c(1, 2)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
# table(dat)
# ftable(dat)
colnames(dat) <- paste0("Q", cols)
write_crosstab(dat, outdir = outdir)
```
# Q2 & Q8
```{r}
cols <- c(2, 6)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
# table(dat)
# ftable(dat)
colnames(dat) <- paste0("Q", cols)
write_crosstab(dat, outdir = outdir)
```


# Q2 & Q8
```{r}
cols <- c(2, 8)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
# table(dat)
# ftable(dat)
colnames(dat) <- paste0("Q", cols)
write_crosstab(dat, outdir = outdir)
```

# Q1 & Q2 & Q12
```{r}
cols <- c(1, 2, 12)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
# ftable(dat)
colnames(dat) <- paste0("Q", cols)
write_crosstab(dat, outdir = outdir)
```


## Q1 & Q3
```{r}
cols <- c(1, 3)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat) <- paste0("Q", cols)
write_crosstab(dat, outdir = outdir)
```
## Q1 & Q4
```{r}
cols <- c(1, 4)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat) <- paste0("Q", cols)
# table(dat)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1 & Q6 & Q7
```{r}
cols <- c(1, 6, 7)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q6 & Q21
```{r}
cols <- c(6, 21)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```


## Q7 & Q21
```{r}
cols <- c(7, 21)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1, Q8 & Q9
```{r}
cols <- c(1, 8, 9)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```
## Q1 & Q10
```{r}
cols <- c(1, 10)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```
## Q1 & Q11
```{r}
cols <- c(1, 11)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```


## Q11 & Q21
```{r}
cols <- c(11, 21)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1, Q12 & Q13
```{r}
cols <- c(1, 12, 13)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1, Q12 & Q21
```{r}
cols <- c(1, 12, 21)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1 & Q14
```{r}
cols <- c(1, 14)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1 & Q15
```{r}
cols <- c(1, 15)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1, Q5 & Q16
```{r}
cols <- c(1, 5, 16)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1, Q17
```{r}
cols <- c(1, 17)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1, Q18
```{r}
cols <- c(1, 18)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```

## Q1, Q16, Q19
```{r}
cols <- c(1, 16, 19)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```
## Q1, Q20 & Q21
```{r}
cols <- c(1, 20, 21)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```


```{r}
cols <- c(1, 22)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```


## Q1, Q23
```{r}
cols <- c(1, 23)
outdir <- file.path(params$outdir, "crosstabs")
dat <- Dat[,cols]
colnames(dat)
colnames(dat) <- paste0("Q", cols)
# ftable(dat)
write_crosstab(dat, outdir = outdir)
```


# Session Info

```{r}
sessionInfo()
```

